Race Science in Mainstream Psychology, 1960-2010

### 2024-05-08 paper/paper.qmd
scales on Silge plots

*[TODO: 
- NHB reviews todo: <https://docs.google.com/document/d/1xzG95pZOZgZQFfSk6yYMFhrnUQ8AWk9U1O5ngm3n_uo/edit>
- copy updated plots
- figure sizes
- align abstract w/ intro
- figures and tables to end
]*

>>>>

*[TODO: 
- NHB reviews todo: <https://docs.google.com/document/d/1xzG95pZOZgZQFfSk6yYMFhrnUQ8AWk9U1O5ngm3n_uo/edit>
- figure out renv::restore()
    - re-make
    - copy updated plots
- figure sizes
- align abstract w/ intro
- figures and tables to end
]*
